Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-04-28 bCFT_paper.tex
Initial commit
[draft]intro content done.

\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

@@

\title{Bipartite Fidelity and Loschmidt echo of bosonic conformal interface}

@@

\section{Introduction}
% the last one to be finished.

@@

@@

\section{A Determinant Identity for the Boundary State Amplitude}
% copy notes app. C

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
% copy notes app. B

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
% copy notes app. A

>>>>

\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\graphicspath{{./}{./images/}}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

@@

\title{Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface}

@@

\section{Introduction}
\input{intro}

@@

% connecting Luttinger liquid(quantum wire) using votage to control the boundary condition. X-ray edge singularity. examples include Taylor santo's topological phases. Hope to have experimental setup. 
There are already numerous theoretical and experimental work on the boundary conditions of Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (Bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent Bosons (two left modes plus two right modes) on the two sides.

@@

\section{A Determinant Identity for the Boundary State Amplitude}
\label{app:pf_of_id}
% copy notes app. C
\input{pf_of_id}

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
\label{app:lambda_12}
% copy notes app. B
\input{lambda_1_lambda_2}

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
\label{app:gnd_dn_lambda}
% copy notes app. A
\input{gnd_dn_lambda}
